\chapter{Introduction}
\label{intro}

\par With our application, "Medical Reports", we have tried to look into how we could help improve the retrieval of patients' information from a remote Electronic Medical Record (EMR) system by incorporating the usage of NFC (Near-Field Communication) tags in the patients' bracelets.

The current solutions for EMR systems do not provide an easy and privacy supportive way of retrieving data about the patients. The most used solution is printing medical reports on paper and using that in order to keep track of the state of the patient. Some of that data might never be recorded, which is also a problem, but the bigger issue is the fact that those files are usually left somewhere in the proximity of the patient, which present a privacy infringement as information can easily be extracted by unauthorized humans.

The second chapter addresses multiple topics regarding the NFC technology and its uses and the privacy. In the first section of chapter 2 we will talk about the NFC technology, what it is and some of its applications. The second section will talk about the NFC technology in Android, how it is currently being used and what the possibilities are. The third section presents the usages of the NFC in specific domains, among which is also the health care system. In section 4 we will talk about some alternatives to NFC in the Health Tech space. Section 5 of this chapter presents the privacy concerns regarding our society in different domains, among which are the health care system and the usage of NFC. Section 6 talks about our proposed solution and what we aim to achieve.

The third chapter presents the architecture that has been implemented in our application as well as a reasoning behind the choices we have made regarding the server application.

In chapter 4 we will present the system requirements in order to run the server application as well as the system requirements for the android application.

In the fifth chapter we created a user manual for the application we have managed to create and we explained some of the logic behind.

The sixth chapter presents what our view on the future of "Medical Reports" application and the improvements that we really think will be necessary in order for this to be a proper solution for an actual implementation in the Health Tech space.

The last chapter, number 7, contains our conclusions about the subject and what we managed to achieve.