\chapter{Potential future improvements}
\label{ch:6}

\par When looking back at the Medical Reports application we managed to create in order to implement the usage of NFC tags in a health care environment we can clearly see some of the improvements that are definitely needed in the future in order for this to be a viable solution.

First of all we need a better design. As straight forward as plain text is in order to communicate the information it is no better than a piece of paper. The application is not very appealing to the end user in its current state, with the exception of some screens.

A second area where we definitely see the place for an improvement is the user registration system. There needs to be a way to notify the users that their account was successfully confirmed, a role has been assigned and that they are able to now login in the mobile application. Perhaps a confirmation email would suffice.

When it comes to the way we are registering patients there should also be an improvement, as at this point we are only allowing the nurse to register a new patient, but not search for the patient in case it already exists and only assign a bracelet instead. In order to achieve this we would need to also collect, at the time of the registration, the social security number of the patient in order to uniquely identify him or her.

As stated in the subsection \ref{sec:ch2sec5subsec3}, in order to preserve the privacy of the data seen on devices we could also add a password or biometric locking mechanism before retrieving the information about a patient from the server in order to once again confirm the fact that the person operating the device is the authorized person, and not someone whom illegally got access to the authorized mobile device. Also we could add special security flags in order to restrict screenshots and screen recordings from the screens that contain sensitive information about the patient.

When it comes to the patients we think an option should be available to retrieve the information without the need of an NFC tag in order to maybe analyze the latest reports, or see in which room the patient is currently located in the hospital.

The reports are surely incomplete as there are many other options that should be available for a medical professional to complete as well as maybe some text fields they can freely complete (like some notes). Also when talking about the reports there should be a way to edit them later (as the author) and they should contain some timestamps that reflect the creation date and the latest update date.

Another improvement we see necessary is the possibility to generate different types of reports, for example a blood test results report that contains different fields than the normal report. While we are still talking about reports a nice to have functionality for the future would be for you to have a small unread icon next to the unread reports in order to notify the medical personnel that there are new reports that have been generated for that patient.

We can also see the possibility of an improvement by adding a settings screen where a profile view would be available for the user as well as a change password option and the Sign Out button.

We know that our solution is not yet complete, however we believe it is good enough at exemplifying what can be done using the NFC tags in order to safely and easily retrieve patient information from an EMR system.